---
title: 'Review 1: BigFive'
output:
  pdf_document: default
  word_document: default
  html_document:
    fig_height: 4
    highlight: pygments
    theme: spacelab
---
### Reg. No: J Gautham & Shivaditya Shivganesh 

### Name:  19BPS1104 & 19BPS1103

* * *
## Aim: To Explore BigFive Dataset

## Setup

```{r}
bigfive <- read.csv('big_five_stocks.csv')
library("tidyverse") 
library('dplyr')
library(psych)
library(vcd)
```


* * *

## Dataset Description

#Name of the Dataset Big Five

#Description of the fields
```{r}
str(bigfive)
```
Name indicates the name of the stock. The open column denotes the opening value of the stock on a particular day. 
The closing column denotes the closing price of the particular stock on given day.

#Check For missing values
```{r}
which(is.na(bigfive))
```


#Basic commands to describe dataset

* * *

1. Daily return of Each stock
```{r}
bigfive <- mutate(bigfive, Return = 100*(close-lag(close))/lag(close) )
bigfive
```

* * *

2. Mean Percentage Return over the years

```{r}
bigfive %>%
  group_by(name) %>%
  summarise(Return = mean(100*(close-lag(close))/lag(close), na.rm = TRUE)) %>%
  arrange(desc(Return))

```
* * *


3. Worst day for each stock

```{r}
bigfive %>%
  group_by(name) %>%
  slice(which.min(close))
```


* * *



```{r}
Google = bigfive[bigfive$name=="GOOGL",]
Amazon = bigfive[bigfive$name=="AMZN",]
Facebook = bigfive[bigfive$name=="FB",]
MicroSoft = bigfive[bigfive$name=="MSFT",]
Apple = bigfive[bigfive$name=="AAPL",]
Index = bigfive[bigfive$name=="^IXIC",]

ggplot(data = bigfive, aes(x=X, y=close, group=name, color = name))+geom_line()
```

